Choosing a Population Genomics Approach

### 2021-12-28 choosing-population-genetics.Rmd
updating some formatting issues

### High coverage individual whole-genome resequencing (hcWGS)  {.unlisted .unnumbered}
**Whole-genome resequencing (WGS)** is where whole genomes of multiple individuals are sequenced and mapped to an assembled reference genome in order to compare variable sites between individuals or populations.
High-coverage (>20x) sequencing is able to find rare variants with high confidence. This approach is considered the is the 'gold standard' for DNA resequencing because it includes all variant types (i.e SNVs, indels, structural variants and CNVs) [@sims2014sequencing].

### Low coverage individual WGS (lcWGS)  {.unlisted .unnumbered}
**Low coverage whole genome sequencing (lcWGS)** is where whole genomes of many individuals are sequenced, but depth of coverage is so low (<5× per site per individual, on average [@nielsen2011genotype]) that individual genotypes cannot be confidently assigned . Instead of assigning specific, “hard called" genotypes, lcWGS data requires probabilistic analyses that account for uncertainty about the true genotype and can incorporate uncertainty across all sequenced samples [@korneliussen2014angsd]. This approach is useful in cases where the research questions of interest are targeted at the population-level (i.e. allele frequencies, linkage disequilibrium (LD) patterns, etc) [@Lou2021-me].

@@

References:

>>>>

### High coverage individual whole-genome resequencing (hcWGS)  {.unlisted .unnumbered}
**Whole-genome resequencing (WGS)** is where whole genomes of multiple individuals are sequenced and mapped to an assembled reference genome in order to compare variable sites between individuals or populations.
High-coverage (>20x) sequencing is able to find rare variants with high confidence. This approach is considered the 'gold standard' for DNA re-sequencing because it includes all variant types (i.e SNVs, indels, structural variants and CNVs) [@sims2014sequencing].

### Low coverage individual WGS (lcWGS)  {.unlisted .unnumbered}
**Low coverage whole genome sequencing (lcWGS)** is where whole genomes of many individuals are sequenced, but depth of coverage is so low (<5× per site per individual, on average [@nielsen2011genotype]) that individual genotypes cannot be confidently assigned. Instead of assigning specific (“hard called") genotypes, lcWGS data requires probabilistic analyses that account for uncertainty about the true genotype and can incorporate uncertainty across all sequenced samples [@korneliussen2014angsd]. This approach is useful in cases where the research questions of interest are targeted at the population-level (i.e. allele frequencies, linkage disequilibrium (LD) patterns, etc) [@Lou2021-me].

@@

# References
